Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-08-12 docs/paper/paper.tex
Format update

\documentclass[10pt]{IEEEtran}

@@

\begin{document}

\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}

\author{Aimen Zelaci, Ahmet Yasli, Cem Kalyoncu, and Huseyin Ademgil}

@@

\begin{abstract}
Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches. However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas, resulting in an exponential increase in the search space. This issue combined with the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take a significant amount of time. As stated in the previous works, artificial neural networks (ANN) can be employed to predict the result of numerical simulations much faster. However, there are two issues with the methods proposed previously: the required number of samples for training and the generality of these methods. In this paper, we propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model. The experimental analysis suggested that the proposed combination not only accurately predicts the confinement loss even with limited amounts of data but also GAN can be used to improve existing methods in the literature. Moreover, the proposed system can also predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset. This property is demonstrated by experimenting on an existing PCF dataset, which the proposed system surpassed the accuracy of the method proposed for it.
\end{abstract}

@@

\begin{figure*}
	\begin{subfigure}{.48\textwidth}
	\centering
    \begin{tikzpicture}
		\begin{axis}[
			xlabel=Epochs, 
			ylabel=Training \space MSE,
			width=\textwidth,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			ymax=3,
			no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_their_data_without.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Without augmentation}
	\end{subfigure}	
	\begin{subfigure}{.48\textwidth}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Epochs, 
			width=\textwidth,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			ymax=3,
			no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_their_data_with.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{With augmentation}
	\end{subfigure}

	\caption{Training MSE of the ANN model with (a) and without (b) GAN phase obtained from SPR dataset}
	\label{chart:trainingmse}
\end{figure*}

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth,
			ymin=5,ymax=7,xmin=5,xmax=7,
			legend pos=south east
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] 
			table{data/spr_their_without_5.txt};
			\addlegendentry{\cite{paper0}}

@@

		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth,
		legend pos=south east
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{data/pcf_their_without_2.txt};
		\addlegendentry{\cite{paper0}}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		legend pos=north west
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/wave_134_their.txt};
	\addlegendentry{\cite{paper0}}

@@

	\addlegendentry{Actual}
	\legend{}
	\end{axis}
	\end{tikzpicture}
	%
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.35}$},
		width=0.48\textwidth,
		legend pos=north west
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/wave_135_their.txt};
  	\addlegendentry{\cite{paper0}}

@@

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth,
			legend pos=south east
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] 
			table{data/spr_our_without_3.txt};
			\addlegendentry{Without GAN}

@@

			\draw[
				line width=1pt,
				solid,color=blue
			]
			(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
			(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
			\addlegendimage{line legend, 
				line width=1pt,
				solid,color=blue}
			\addlegendentry{$Actual$}
			\legend{}
		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth,
		legend pos=south east
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{data/pcf_our_without_4.txt};
		\addlegendentry{Without GAN}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		legend pos=north east,
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/wave_134_our.txt};
	\addlegendentry{Without GAN}

@@

	\addplot[
		color=blue
	] 
	table[x={wave},y={real}]{data/wave_134_our.txt};
	\addlegendentry{Actual}\legend{};
	\end{axis}
	\end{tikzpicture}
	%
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.33}$},
		width=0.48\textwidth,
		legend pos=north east
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/wave_133_our.txt};
	\addlegendentry{Without GAN}

@@

\begin{table}
\caption{Detailed performance analysis}
\begin{tabular}{l|l|l|l|l|l|l}
	Method & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
	Dataset & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
	GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline
	Average   			& \textbf{0.314} & 0.894 & 0.987   &   \textbf{0.134} & 0.156          & 0.167 \\
	Best      			& \textbf{0.006} & 0.042 & 0.047   &   0.095          & \textbf{0.093} & 0.106 \\
	Worst     			& \textbf{1.102} & 6.792 & 5.955   &   \textbf{0.181} & 0.265          & 0.416 \\
	Std. dev.       	& \textbf{0.437} & 2.213 & 1.940   &   \textbf{0.031} & 0.046          & 0.090 \\
\end{tabular}
\label{tbl:all}
\end{table}

@@

\begin{table}
\caption{Execution time of algorithms}
\begin{tabular}{l|l|l}
Method    			  &  Training (s) & Testing (ms) \\\hline
Proposed ANN 		  &  42 & 3.6 \\
Proposed ANN with GAN & 449 & 3.6 \\
GAN phase only        & 370 &  -  \\
\cite{paper0}		  &  20 & 2.7 \\
FV-FEM		   		  &  -  & 106958
\end{tabular}
\label{tbl:timing}
\end{table}

>>>>

\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{jsen}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{wrapfig}
\usepackage{placeins}
\usepackage[outdir=./]{epstopdf}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\markboth{\journalname, VOL. XX, NO. XX, XXXX 2017}
{Author \MakeLowercase{\textit{et al.}}: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS (February 2017)}
\definecolor{abstractbg}{rgb}{0.89804,0.94510,0.83137}
\setlength{\fboxrule}{0pt}
\setlength{\fboxsep}{0pt}

@@

\begin{document}
\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}
\author{
	Aimen Zelaci, Ahmet Yasli, Cem Kalyoncu, and Huseyin Ademgil, \IEEEmembership{Senior Member, IEEE}
	\thanks{A. Z. Author is with 
		the European University of Lefke, Faculty of Engineering, Electrical and Electronics Engineering Department, Lefke, TR-10, Turkey (e-mail: aimen.zelaci@gmail.com).
	}
	\thanks{A. Y. Author is with 
		the European University of Lefke, Faculty of Engineering, Electrical and Electronics Engineering Department, Lefke, TR-10, Turkey (e-mail: ayasli@eul.edu.tr).
	}
	\thanks{C. K. Author is with 
		the European University of Lefke, Faculty of Engineering, Computer Engineering Department, Lefke, TR-10, Turkey (e-mail: ckalyoncu@eul.edu.tr).
	}
	\thanks{H. A. Author is with 
		the European University of Lefke, Faculty of Engineering, Computer Engineering Department, Lefke, TR-10, Turkey (e-mail: hademgil@eul.edu.tr).
	}
}

\IEEEtitleabstractindextext{%
\fcolorbox{abstractbg}{abstractbg}{%
\begin{minipage}{\textwidth}%
%\begin{wrapfigure}[12]{r}{3in}%
%\includegraphics[width=3in]{jsenga.png}%
%\end{wrapfigure}%
\begin{abstract}
Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches. However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas, resulting in an exponential increase in the search space. This issue combined with the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take a significant amount of time. As stated in the previous works, artificial neural networks (ANN) can be employed to predict the result of numerical simulations much faster. However, there are two issues with the methods proposed previously: the required number of samples for training and the generality of these methods. In this paper, we propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model. The experimental analysis suggested that the proposed combination not only accurately predicts the confinement loss even with limited amounts of data but also GAN can be used to improve existing methods in the literature. Moreover, the proposed system can also predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset. This property is demonstrated by experimenting on an existing PCF dataset, which the proposed system surpassed the accuracy of the method proposed for it.
\end{abstract}

\begin{IEEEkeywords}
Artificial neural network (ANN), fiber optic sensor, generative adversarial networks (GAN), machine learning, photonic crystal fiber (PCF), surface plasmon resonance (SPR).
\end{IEEEkeywords}
\end{minipage}}}

@@

@@

\begin{figure}
	\begin{subfigure}{.48\textwidth}
	\centering
    \begin{tikzpicture}
		\begin{axis}[
			xlabel=Epochs, 
			ylabel=Training \space MSE,
			width=\textwidth,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			ymax=3,
			height=6cm,
			no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_their_data_without.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Without augmentation}
	\end{subfigure}	
	\begin{subfigure}{.48\textwidth}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Epochs, 
			ylabel=Training \space MSE,
			width=\textwidth,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			ymax=3,
			height=6cm,
			no marks
		]
		\addplot[line width=1pt,solid,color=blue] %
		table{data/ann_tr_loss_3k_their_data_with.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{With augmentation}
	\end{subfigure}

	\caption{Training MSE of the ANN model with (a) and without (b) GAN phase obtained from SPR dataset}
	\label{chart:trainingmse}
\end{figure}

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth,			
			height=8cm,
			ymin=5,ymax=7,xmin=5,xmax=7,
			legend pos=south east
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] 
			table{data/spr_their_without_5.txt};
			\addlegendentry{\cite{paper0}}

@@

		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth,
		height=8cm,
		legend pos=south east
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{data/pcf_their_without_2.txt};
		\addlegendentry{\cite{paper0}}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		height=8cm,
		legend pos=north west
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/wave_134_their.txt};
	\addlegendentry{\cite{paper0}}

@@

	\addlegendentry{Actual}
	\legend{}
	\end{axis}
	\end{tikzpicture}
	%
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.35}$},
		width=0.48\textwidth,
		height=8cm,
		legend pos=north west
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/wave_135_their.txt};
  	\addlegendentry{\cite{paper0}}

@@

\begin{figure*}
\begin{subfigure}{0.48\textwidth}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=Actual loss in $log(db/cm)$, 
			ylabel=Predicted loss in $log(db/cm)$,
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=\textwidth,
%			height=6cm,
			legend pos=south east
		]
			\addplot[
				only marks,
				mark size=2.9pt, mark=o, color=red, fill=red
			] 
			table{data/spr_our_without_3.txt};
			\addlegendentry{Without GAN}

@@

			\draw[
				line width=1pt,
				solid,color=blue
			]
			(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
			(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
			\addlegendimage{line legend, 
				line width=1pt,
				solid,color=blue}
			\addlegendentry{$Actual$}
			\legend{}
		\end{axis}
	\end{tikzpicture}
	\caption{SPR dataset}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
    \begin{tikzpicture}
	\begin{axis}[
		xlabel=Actual loss in $log(db/cm)$, 
		ylabel=Predicted loss in $log(db/cm)$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=\textwidth,
%		height=6cm,
		legend pos=south east
	]
		\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table{data/pcf_our_without_4.txt};
		\addlegendentry{Without GAN}

@@

\begin{subfigure}{\textwidth}
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		legend pos=north east,
%		height=6cm
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	]
	table[x={wave},y={predicted}]{data/wave_134_our.txt};
	\addlegendentry{Without GAN}

@@

	\addplot[
		color=blue
	] 
	table[x={wave},y={real}]{data/wave_134_our.txt};
	\addlegendentry{Actual}\legend{};
	\end{axis}
	\end{tikzpicture}
	%
	\begin{tikzpicture}
	\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.33}$},
		width=0.48\textwidth,
		legend pos=north east,
%		height=6cm
	]
	\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
	] 
	table[x={wave},y={predicted}]{data/wave_133_our.txt};
	\addlegendentry{Without GAN}

@@

\begin{table}
\caption{Detailed performance analysis}
\centering
\begin{tabular}{l|l|l|l|l|l|l}
	Method & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
	Dataset & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
	GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline
	Average   			& \textbf{0.314} & 0.894 & 0.987   &   \textbf{0.134} & 0.156          & 0.167 \\
	Best      			& \textbf{0.006} & 0.042 & 0.047   &   0.095          & \textbf{0.093} & 0.106 \\
	Worst     			& \textbf{1.102} & 6.792 & 5.955   &   \textbf{0.181} & 0.265          & 0.416 \\
	Std. dev.       	& \textbf{0.437} & 2.213 & 1.940   &   \textbf{0.031} & 0.046          & 0.090 \\
\end{tabular}
\label{tbl:all}
\end{table}

@@

\begin{table}
\caption{Execution time of algorithms}
\centering
\begin{tabular}{l|l|l}
Method    			  &  Training (s) & Testing (ms) \\\hline
Proposed ANN 		  &  42 & 3.6 \\
Proposed ANN with GAN & 449 & 3.6 \\
GAN phase only        & 370 &  -  \\
\cite{paper0}		  &  20 & 2.7 \\
FV-FEM		   		  &  -  & 106958
\end{tabular}
\label{tbl:timing}
\end{table}
